Quantifying and Modeling Global Water Accessibility including Water Typology

### 2021-01-20 docs/manuscript/manuscript.tex
Updates from Overleaf

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{adv-cor-plot}
  \caption{Correlation graph of numerical variables}
  \label{fig:year}
\end{figure}

>>>>

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{adv-cor-plot}
  \caption{Correlation graph of numerical variables}
  \label{fig:year}
\end{figure}
Additionally, we wanted to explore if the modes of transportation variables have any relationship with potential water variables. Therefore, we investigated by developing more correlation plots relating transportation variables with water accessibility variables which is shown in Figure .

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{transportation-time}
  \caption{Correlation graph of numerical variables}
  \label{fig:year}
\end{figure}
